Increasing User Engagement in a Volunteer-Based Ephemeral Evolutionary Computation System

### 2017-02-16 2017-EUROPAR/Gamification/paper.tex
Figures uploaded with dummy captions
@JJ Please have a look

\documentclass{llncs}
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{url}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\sloppy

@@

>>>>

\documentclass{llncs}
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{url}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{subfigure}
\begin{document}
\sloppy

@@

\section{Experiments}
\label{sec:experiments}

\subsection{Results}
\label{sec:results}

\begin{figure*}[t]
    \centering
    \subfigure  [6 workers]
    {
        \includegraphics[width=4in]{img/puts_user.png}
    }
    \subfigure  [12 workers]
    {
        \includegraphics[width=4in]{img/puts_ip.png}
    }

    \caption{100 experiments with random parameters for the 128 Bit Griewank 
    single-objective optimization test function. Experiments are ranked by 
    the mean time to solution of 5 runs, with (a) 6 workers, and (b) 12 workers.}
    \label{fig:griewank}
\end{figure*}

\begin{figure*}[t]
    \centering
        \includegraphics[width=4in]{img/puts_box.png}
    \caption{Comparison of 30 runs of the 128 Bit OneMax problem. 
    Box-plot of the number of evaluations needed for solution, with a 2, 6 and 12 workers
    homogeneous configuration on the left side, and Heterogeneous configuration on the
    right side of each.
    }
    \label{fig:comp-onemax}
\end{figure*}

\begin{figure*}[t]
    \centering
        \includegraphics[width=5in]{img/puts_by_time.png}
    \caption{Comparison of 30 runs of the 128 Bit OneMax problem. 
    Box-plot of the number of evaluations needed for solution, with a 2, 6 and 12 workers
    homogeneous configuration on the left side, and Heterogeneous configuration on the
    right side of each.
    }
    \label{fig:comp-onemax}
\end{figure*}
\begin{figure*}[t]
    \centering
        \includegraphics[width=5in]{img/workers_best_user.png}
    \caption{Comparison of 30 runs of the 128 Bit OneMax problem. 
    Box-plot of the number of evaluations needed for solution, with a 2, 6 and 12 workers
    homogeneous configuration on the left side, and Heterogeneous configuration on the
    right side of each.
    }
    \label{fig:comp-onemax}
\end{figure*}
\begin{figure*}[t]
    \centering
        \includegraphics[width=5in]{img/workers_put_ip.png}
    \caption{Comparison of 30 runs of the 128 Bit OneMax problem. 
    Box-plot of the number of evaluations needed for solution, with a 2, 6 and 12 workers
    homogeneous configuration on the left side, and Heterogeneous configuration on the
    right side of each.
    }
    \label{fig:comp-onemax}
\end{figure*}
